Lobbying and Legislative Uncertainty

### 2016-05-10 presentation.tex
remove B subscript on a few X's since I don't use it elsewhere in presentation

\pause
\begin{enumerate}[<+->]
	\item In the U.S., about $\$ 4$ billion / yr spent on lobbying and campaign contributions
	\item There is usually lobbying on both sides of a given issue
	\item Moderate legislators receive more contributions than those that are ideologically extreme
	\item Legislators about whom there is a moderate level of uncertainty are lobbied the most
\end{enumerate}

@@

\subsection{Simultaneous Model}
\begin{frame}{What I know...}
\pause
FOCs look the same for Vote Buyer B, e.g.
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item Either one root at zero, or
			\pause
			\item Two roots and only larger one (at $X_B>0$?) satisfies SOC
		\end{itemize}

\vskip.1in
\pause
For Vote Buyer A,
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{1}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item One root: zero or $X_B<0$
		\end{itemize}

>>>>

\pause
\begin{enumerate}[<+->]
	\item In the U.S., about $\$ 4$ billion / yr spent on lobbying and campaign contributions
	\item There is usually lobbying on both sides of a given issue
	\item Moderate legislators receive more contributions than those who are ideologically extreme
	\item Legislators about whom there is a moderate level of uncertainty are lobbied the most
\end{enumerate}

@@

\subsection{Simultaneous Model}
\begin{frame}{What I know...}
\pause
FOCs look the same for Vote Buyer B, e.g.
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item Either one root at zero, or
			\pause
			\item Two roots and only larger one (at $X>0$?) satisfies SOC
		\end{itemize}

\vskip.1in
\pause
For Vote Buyer A,
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{1}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item One root: zero or $X<0$
		\end{itemize}
